---
title: "Scenario 6"
format: revealjs
editor: visual
---

## Background

This document is almost identical to the quarto document from Scenario 4, but now I am just changing the format to a presentation. See how the information shows up on the slides.

## Install Packages (if necessary)

```{r installing packages}
#| echo: true
 
# install.packages("tidyverse") # will take some times since multiple packages in one
# install.packages("ggridges")
# install.packages("janitor")
```

## Calling all libraries

```{r calling libraries}
#| echo: true

library(tidyverse)
library(ggridges)
library(janitor)

```

## Bringing in the data

```{r uploadind data}
#| echo: true

wnba_2019_per_game_stats <- read_csv("Data/2019_wbna_per_game_stats.csv") |> 
  clean_names() # just want to make the names all lower case and camel case style

```

I am going to focus on the 3-point attempts per game stat and look at differences by position in this season.

## The before times

Here is a histogram with mini plots separated

```{r histogram 1}

ggplot(wnba_2019_per_game_stats, aes(x = x3pa)) +
  geom_histogram() +
  facet_wrap(pos ~.) +
  labs(title = "3-Point Field Goal Attempts Per Game")

```

## The before times (cont.)

And here they are all in one line

```{r histogram 2}
ggplot(wnba_2019_per_game_stats, aes(x = x3pa)) +
  geom_histogram() +
  facet_grid (pos ~.) + # facet_grid gives you a different visual than facet_wrap
  labs(title = "3-Point Field Goal Attempts Per Game")
```

## The before times (cont.)

Either one, I don't have a sense of what I am looking at. I would need to adjust the bins as well to make it clearer and do some extra work with the axis to make it less cluttered.

## The after times

Here is the same data in density plots

```{r density plot}

# I am adding a y variable here
ggplot(wnba_2019_per_game_stats, aes(x = x3pa, y = pos)) +
  # and I am changing the plot type here
  geom_density_ridges() +
  labs(title = "3-Point Field Goal Attempts Per Game")

```

I can tell the differences in 3-point attempts by position much easier with this plot.

## There you go! 

This was a really basic presentation just to show how easy it can be to take your documents and put them into slides. You can learn a lot more about formatting in quarto from the community and [the quatro website](https://quarto.org/docs/presentations/revealjs/). 
