---
title: "Scenario 4"
format: html
editor: visual
---

## Install Packages (if necessary) 
```{r installing packages}
# install.packages("tidyverse") # will take some times since multiple packages in one
# install.packages("ggridges")
# install.packages("janitor")
```

## Calling all libraries 

```{r calling libraries}

library(tidyverse)
library(ggridges)
library(janitor)

```
## Bringing in the data

```{r uploadind data}

wnba_2019_per_game_stats <- read_csv("Data/2019_wbna_per_game_stats.csv") |> 
  clean_names() # just want to make the names all lower case and camel case style

```
I am going to focus on the 3-point attempts per game stat and look at differences by position in this season.

## The before times

Here is a histogram with mini plots separated

```{r histogram 1}

ggplot(wnba_2019_per_game_stats, aes(x = x3pa)) +
  geom_histogram() +
  facet_wrap(pos ~.) +
  labs(title = "3-Point Field Goal Attempts Per Game")

```
And here they are all in one line
```{r histogram 2}
ggplot(wnba_2019_per_game_stats, aes(x = x3pa)) +
  geom_histogram() +
  facet_grid (pos ~.) + # facet_grid gives you a different visual than facet_wrap
  labs(title = "3-Point Field Goal Attempts Per Game")

```
Either one, I don't have a sense of what I am looking at. I would need to adjust the bins as well to make it clearer and do some extra work with the axis to make it less cluttered. 

## The after times

Here is the same data in density plots

```{r density plot}

# I am adding a y variable here
ggplot(wnba_2019_per_game_stats, aes(x = x3pa, y = pos)) +
  # and I am changing the plot type here
  geom_density_ridges() +
  labs(title = "3-Point Field Goal Attempts Per Game")

```
I can tell the differences in 3-point attempts by position much easier with this plot. 
