---
title: "Scenario 5"
format: html
editor: visual
---
NOTE: If you are following scenario 4, the plot is the same last density plot. 

## Install Packages (if necessary) 
```{r installing packages}
# install.packages("tidyverse") # will take some times since multiple packages in one
# install.packages("ggridges")
# install.packages("janitor")
```

## Calling all libraries 

```{r calling libraries}

library(tidyverse)
library(ggridges)
library(janitor)

```
## Bringing in the data

```{r uploadind data}

wnba_2019_per_game_stats <- read_csv("Data/2019_wbna_per_game_stats.csv") |> 
  clean_names() # just want to make the names all lower case and camel case style

```
I am going to focus on the 3-point attempts per game stat and look at differences by position in this season.

Let's save the last density plot using ggsave

# Creating the plot and saving it
```{r density plot}

density_plot <- ggplot(wnba_2019_per_game_stats, aes(x = x3pa, y = pos)) +
  geom_density_ridges() +
  labs(title = "3-Point Field Goal Attempts Per Game")

ggsave("Outputs/scenario_5_density_plot.png")

```
You can also adjust the size and which plot to save! Check out the documentation 

```{r}

help(ggsave)

```

